### 2024-05-27 fantasy-football.qmd
20240521 - remove git lfs
20240527 - audience and number of players

### The Objective {#sec-football}

@@

As noted in the [Introduction](intro.qmd), fantasy football is an online game where participants assemble (i.e., "draft") imaginary teams composed of real-life National Football League (NFL) players.^[Fantasy leagues are also available for [baseball](https://en.wikipedia.org/wiki/Fantasy_baseball), [basketball](https://en.wikipedia.org/wiki/Fantasy_basketball), and many other sports.]
The participants are in charge of managing and making strategic decisions for their imaginary team to have the best possible team that will score the most points.
Thus, the participants are called "managers".
Managers make decisions such as selecting which players to draft, selecting which players to play (i.e., "start") on a weekly basis, identifying players to pick up from the remaining pool of available players (i.e., waiver wire), and making trades with other teams.
Fantasy football relies heavily on prediction—trying to predict which players will perform best and selecting them accordingly.

>>>>

Football is the most widely watched sport in the United States.^[https://news.gallup.com/poll/610046/football-retains-dominant-position-favorite-sport.aspx (archived at https://perma.cc/X2UG-RAAK); https://www.statista.com/statistics/1430289/most-watched-sports-leagues-usa/ (archived at https://perma.cc/JNU6-S96A)]

### The Objective {#sec-footballObjective}

@@

Fantasy football is one of the most widely played games in the history of games.
It is estimated that around 29–60 million people play fantasy football.^[https://thefsga.org/industry-demographics/ (archived at https://perma.cc/9PB8-ZDJJ); https://www.statista.com/topics/10895/fantasy-sports-in-the-us/ (archived at https://perma.cc/8YSN-UUNT)]
As noted in the [Introduction](intro.qmd), fantasy football is an online game where participants assemble (i.e., "draft") imaginary teams composed of real-life National Football League (NFL) players.^[Fantasy leagues are also available for [baseball](https://en.wikipedia.org/wiki/Fantasy_baseball), [basketball](https://en.wikipedia.org/wiki/Fantasy_basketball), and many other sports.]
The participants are in charge of managing and making strategic decisions for their imaginary team to have the best possible team that will score the most points.
Thus, the participants are called "managers".
Managers make decisions such as selecting which players to draft, selecting which players to play (i.e., "start") on a weekly basis, identifying players to pick up from the remaining pool of available players (i.e., waiver wire), and making trades with other teams.
Fantasy football relies heavily on prediction—trying to predict which players will perform best and selecting them accordingly.
